%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  % %---------------------------------------------------------
  \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
  $^*$ equal contribution, $^\#$ alphabetical ordering
  \end{cvitems}}

      %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
  \textbf{Jagadish, A. K.}*, Strittmatter, Y.*,  Jacoby, N., Kachergis, G., Schulz, E., Daw, N., Chandramouli, S. H., \& Griffiths, T. (2026). Closing the Loop to Discover Psychological Theories with an Automated Cognitive Scientist. {Preprint}\\
  \href{https://arxiv.org/abs/2606.26448}{[PDF]}
  \end{cvitems}}

    %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Zhang, L., \textbf{Jagadish, A. K.}, Lake, B., \& Griffiths, T. (2026). Using Probabilistic Programs to Train Inductive Reasoning in Large Language Models. {Preprint}\\
  \href{https://arxiv.org/pdf/2606.09856}{[PDF]}
  \end{cvitems}}
  %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Binz, M., ..., \textbf{Jagadish, A. K.}$^\#$,..., \& Schulz, E. (2026). Post-training makes large language models less human-like. {Preprint}\\
  \href{https://arxiv.org/pdf/2605.07632}{[PDF]}
  \end{cvitems}}
    %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
  Chandramouli, S., Kachergis, G., \textbf{Jagadish, A. K.} (2026). Automated Adversarial Collaboration for Advancing Theory Building in the Cognitive Sciences. {In the 9th Annual Conference Cognitive Computational Neuroscience}\\
  \href{https://arxiv.org/pdf/2604.25521}{[PDF]}
  \end{cvitems}}
    %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Xie, H., \textbf{Jagadish, A. K.}, Pan, L., Wilson, R. C. (2026). Think-Aloud Reshapes Automated Cognitive Model Discovery Beyond Behavior. {In the 9th Annual Conference Cognitive Computational Neuroscience}\\
  \href{https://arxiv.org/pdf/2605.05091}{[PDF]}
  \end{cvitems}}
  %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
  \textbf{Jagadish, A. K.}, Witte, K., Mathony, M., Binz, M., \& Schulz, E. (2026). Can we automatize scientific discovery in the cognitive sciences? {Preprint}\\
  \href{https://arxiv.org/abs/2603.20988}{[PDF]}
  \end{cvitems}}

%---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Braga, D., Marjieh, R.$^*$, \textbf{Jagadish, A. K.}$^*$, Sucholutsky, I., Jacoby, N., \&  Griffiths, T. L. (2026). Automated Discovery of Psychological Representations using Language Model Agents. {In the Proceedings of the Annual Meeting of the Cognitive Science Society} \href{https://drive.google.com/file/d/1NQ0tgUqLk8KDsJfXqCQgLiGnnDbjQ50X/view?usp=sharing}{[PDF]}\\
  \end{cvitems}}
%---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   \textbf{Jagadish, A. K.}$^*$, Rmus, M.$^*$, Mathony, M., \& Schulz, E. (2026). Modeling individual differences in learning and memory using large language models. \\
  {In the Proceedings of the Annual Meeting of the Cognitive Science Society} \href{https://drive.google.com/file/d/1CcB55nqqBrzAb1TAl21NZrLaD-VclmLo/view?usp=sharing}{[PDF]}
  \end{cvitems}}
%---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Strittmatter, Y., Griffiths, T. L., \& \textbf{Jagadish, A. K.} (2026). Pipeline for systematic curation of human experiments. {In the Proceedings of the Annual Meeting of the Cognitive Science Society}  \href{https://drive.google.com/file/d/1fIvK43MxyiOtc13B7JDwyvzfzIulutVA/view?usp=sharing}{[PDF]}\\
  \end{cvitems}}

  %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   \textbf{Jagadish, A. K.}, Thalmann, M., Coda-Forno, J., Binz, M. \& Schulz, E. (2025). Meta-learning ecological priors from large language models captures human learning and decision making. \\
  {Preprint}
  \href{https://arxiv.org/abs/2509.00116}{[PDF]}
  \end{cvitems}}
%---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Rmus, M.$^*$, \textbf{Jagadish, A. K.}$^*$, Mathony, M., \& Schulz, E. (2025). Generating computational cognitive models using large language models. \\
  {In the 39th Annual Conference on Neural Information Processing Systems (NeurIPS)}
  \href{https://arxiv.org/pdf/2502.00879.pdf}{[PDF]}
  \end{cvitems}}
%---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Binz, M., \textbf{Jagadish, A. K.}, Rmus, M., \& Schulz, E. (2025). Automated scientific minimization of regret. \\
  {In the AI4Science Workshop at the 39th Annual Conference on Neural Information Processing Systems (NeurIPS)}
  \href{https://arxiv.org/pdf/2505.17661}{[PDF]}
  \end{cvitems}}
%---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Cohen, Z.$^*$, \textbf{Jagadish, A. K.}$^*$, Hosseini, E.$^*$, \& Eckstein, M. (2025). Reinforcement learning: computational modeling of learning and decision-making \\
  {Lecture Notes of the Analytical Connectionism Summer School 2023 and 2024. Proceedings of Machine Learning Research (PMLR)}
  \href{https://drive.google.com/file/d/1h3gfx7hr-9iR11brSEr1IvfeW-Ri2wCA/view?usp=sharing}{[PDF]}
  \end{cvitems}}
%---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
  \textbf{Jagadish, A. K.}, Thalmann, M., Coda-Forno, J., Binz, M. \& Schulz, E. Bounded ecologically rational meta-learned inference explains human category learning. (2025). \\
  {Proceedings of the Annual Meeting of the Cognitive Science Society}
  \href{https://escholarship.org/uc/item/7k85s0j0}{[PDF]}
  \end{cvitems}}
 %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
  Binz, M., ..., \textbf{Jagadish, A. K.}$^\#$,..., \& Schulz, E. (2025). Centaur: a foundation model of human cognition.\\
  {Nature} \href{https://akjagadish.github.io/assets/Centaur_3_1__a_foundation_model_of_human_cognition.pdf}{[PDF]} 
  % \href{https://arxiv.org/pdf/2402.01821.pdf}{[PDF]}
  \end{cvitems}}

 %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Demirican, C.$^*$, Saanum, T.$^*$, \textbf{Jagadish, A. K.},  Binz, M., \& Schulz, E. (2025). Sparse autoencoders reveal temporal difference learning in large language models. \\
  {In the 13th International Conference on Learning Representations (ICLR)} 
  \href{https://arxiv.org/pdf/2410.01280}{[PDF]} 
  % \href{https://arxiv.org/pdf/2402.01821.pdf}{[PDF]}
  \end{cvitems}}
  
 %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   \textbf{Jagadish, A. K.}, Coda-Forno, J., Thalmann, M., Schulz, E., \& Binz, M. (2024). Human-like category learning by injecting ecological priors from large language models into neural networks.\\
  {In the 41st International Conference on Machine Learning (ICML)}
  \href{https://arxiv.org/pdf/2402.01821.pdf}{[PDF]}
  \end{cvitems}}
 %---------------------------------------------------------
 
   %\\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Schubert, J., \textbf{Jagadish, A. K.}, Binz, M., \& Schulz, E. (2024). In-context learning agents are asymmetric belief updaters.\\
  {Proceedings of the 41st International Conference on Machine Learning (ICML)}
\href{https://arxiv.org/pdf/2402.03969.pdf}{[PDF]}
% \href{https://drive.google.com/file/d/1yuGbsc9yABiiuVD9alxI1u63usa_aDgr/view?usp=sharing}{[Abstract@CCN-2023]}
  \end{cvitems}}
 %---------------------------------------------------------


  %\\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   \textbf{Jagadish, A. K.}, Binz, M., Saanum, T., Wang, J. X., \& Schulz, E. (2024). Zero-shot compositional reasoning in a reinforcement learning setting. 
  {Preprint}
  \href{https://osf.io/preprints/psyarxiv/ymve5}{[PDF]}
  \end{cvitems}}
   %---------------------------------------------------------
   
  %\\[0.35cm]
  \cventryPub{
  \begin{cvitems}
     Ben-Zion, Z., Witte, K.$^*$, \textbf{Jagadish, A. K.}$^*$, Duek, O., Harpaz-Rotem, I., Khorsandian, M., ... \& Spiller, T. R. (2024). “Chat-GPT on the couch”: assessing and alleviating state anxiety in large language models.
  {npj Digital Medicine}
  \href{https://osf.io/preprints/psyarxiv/j7fwb}{[PDF]}
  \end{cvitems}}
   %---------------------------------------------------------
   
  \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Coda-Forno, J.$^*$, Witte, K.$^*$, \textbf{Jagadish, A. K.}, Binz, M., Akata, Z., \& Schulz, E. (2023). Inducing anxiety in large language models increases exploration and bias.
  {Preprint}
  \href{https://arxiv.org/abs/2304.11111}{[PDF]}
  \end{cvitems}}
 %---------------------------------------------------------
  \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
    Binz, M.,  Dasgupta, I., \textbf{Jagadish, A. K.}, Botvinick, M., Wang, J.X., \& Schulz, E. (2023). Meta-learned models of cognition.  \hfill \break
  {Behavioral and Brain Sciences}
  \href{https://arxiv.org/abs/2304.06729}{[PDF]}
  \end{cvitems}}
 %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   Schubert, J., \textbf{Jagadish, A. K.}, Binz, M., \& Schulz, E. (2023). A rational analysis of optimism bias using meta-reinforcement learning.
  {In the 6th Annual Conference on Cognitive Computational Neuroscience (CCN)}
  \href{https://drive.google.com/file/d/1yuGbsc9yABiiuVD9alxI1u63usa_aDgr/view?usp=sharing}{[PDF]}
  \end{cvitems}}
 %---------------------------------------------------------
   \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
  \textbf{Jagadish, A. K.}, Saanum, T., Wang, J. X., Binz, M., \& Schulz, E. (2022). Probing compositional inference in natural and artificial agents. 
  {In 5th Multidisciplinary Conference on Reinforcement Learning and Decision Making (RLDM)}
  \end{cvitems}}
  %---------------------------------------------------------
  %\\[0.35cm]
  
  \cventryPub{
  \begin{cvitems}
   Bashiri, M.$^*$, Walker, E.$^*$, Lurz, K. K., \textbf{Jagadish, A. K.}, Muhammad, T., Ding, Z., ... \& Sinz, F. (2021). A flow-based latent state generative model of neural population responses to natural images. 
   {In Advances in Neural Information Processing Systems (NeurIPS)}
  \href{https://proceedings.neurips.cc/paper/2021/file/84a529a92de322be42dd3365afd54f91-Paper.pdf}{[PDF]}
  \end{cvitems}}
  
  %  %---------------------------------------------------------
 %\\[0.35cm]
 
  \cventryPub{
  \begin{cvitems}
   Lurz, K. K., Bashiri, M., Willeke, K. F., \textbf{Jagadish, A. K.}, Wang, E., Walker, E. Y., ... \& Sinz, F. (2021). Generalization in data-driven models of primary visual cortex. 
   {In International Conference on Learning Representations (ICLR)}
  \href{https://doi.org/10.1101/2020.10.05.326256}{[PDF]}
  \end{cvitems}}
   % ---------------------------------------------------------
  \\[0.35cm]
  
  \cventryPub{
  \begin{cvitems}
   Rodriguez, C.$^*$, \textbf{Jagadish, A. K.}$^*$, Meskaldji, D. E., Haller, S., Herrmann, F., Van De Ville, D., \& Giannakopoulos, P. (2019). Structural correlates of personality dimensions in healthy aging and MCI. {Frontiers in psychology}
  \href{https://doi.org/10.3389/fpsyg.2018.02652}{[PDF]}
  \end{cvitems}}
%   %---------------------------------------------------------
%   \\[0.35cm]
%   \cventryPub{
%   \begin{cvitems}
%     Annadani, Y., Naganoor, V., \textbf{Jagadish, A. K.}, \& Chemmangat, K. (2016). Selfie detection by synergy-constraint based convolutional neural network.  {In 2016 12th International Conference on Signal-Image Technology \& Internet-Based Systems (SITIS), IEEE}
% \href{https://www.semanticscholar.org/reader/b8f3f6d8f188f65ca8ea2725b248397c7d1e662d}{[PDF]}
%   \end{cvitems}}  
  %---------------------------------------------------------
  \\[0.35cm]
  \cventryPub{
  \begin{cvitems}
   \textbf{Jagadish, A. K.}, Goswami, S., Saha, P., Chakrabarty, S., \& Rajgopal, K. (2016). Artificial Bee Colony (ABC) based variable density sampling scheme for CS-MRI. In 2016 {IEEE Region 10 Conference (TENCON)}
  \href{https://doi.org/10.1109/TENCON.2016.7848212}{[PDF]}
  \end{cvitems}}
\vspace{3mm}
\end{cventries}
